\section{Acknowledgements}
Very special thanks go to Osama Abuzaid for tremendously useful conceptual discussions, co-developing security notions and proofs etc. in 2020. Not all of the discussions have found their way into this document (yet) and some of the definitions have evolved from the time that we discussed them with Osama, but Osama's insights shaped and enriched our thinking in many tangible concrete ways as well as on a general level towards writing this document.

We are greatful to Eric Cornelissen, Eljon Harlicaj, Pihla Karanko and Joonas von Lerber for suggestions and careful proof-reading of the the book in its various forms, and Amirhosein Rajabi for useful feedback on Appendix B. We thank Christoph Egger and Kirthivaasan Puniamurthy for many helpful discussions on state-separating proofs, some of which also appear in this proof viewer project~\cite{ACNS:BEP24}. We thank Jan Winkelmann for inspiring discussions especially on notation and, in particular, for suggesting to list state and parameters explicitly in the package definitions. We thank Konrad Kohbrok and Markulf Kohlweiss for useful discussions and suggestions regarding the code-structuring and further formalizations. We thank Estuardo Alpirez Bock and Miika Leinonen for suggestions on the didactics and order of presentation. Last, but not least, thanks to all course participants who contributed to the improvement of the document by enriching our understanding of learning.

(Some of the acknowledgements are missing. If you feel you have contributed to the book, we would be very happy to add your name here.)