\subsection{Theorems on symmetric encryption schemes}
\paragraph{Constructing symmetric encryption schemes}
We describe how to build secure symmetric encryption schemes. We start with IND-CPA security
and then turn to AE-security. Since PRFs and PRPs tend to operate on blocks, we will often
need an \emph{encoding} scheme which encodes messages into a multiple of the block length.
\begin{definition}[Encoding scheme]
We call two functions $\O{encode}_\lambda:\bin^*\rightarrow\bin^*$ and $\O{decode}_\lambda:\bin^*\rightarrow\bin^*$
an \emph{encoding scheme} if
\begin{itemize}
\item $\O{encode}_\lambda$ and $\O{decode}_\lambda$ are computable in polynomial time polynomial in $\lambda$ and the length of the input.
\item $\O{decode}_\lambda$ is the inverse of $\O{encode}_\lambda$, i.e., for all $x\in\bin^*$, we have
      $\O{decode}_\lambda(\O{encode}_\lambda(x))=x$. In particular, $\O{encode}_\lambda$ is \emph{injective}, i.e., if $x\neq x'$, then $\O{encode}_\lambda(x)\neq\O{encode}_\lambda(x')$.
\item the length $\O{encode}_\lambda$ only depends on the length of the input, i.e., if $\abs{x}=\abs{x'}$, then 
$\abs{\O{encode}_\lambda(x)}=\abs{\O{encode}_\lambda(x')}$.
\item for all $x\in\bin^*$, $\abs{\O{encode}_\lambda(x)}$ is divisible by $\lambda$.
\end{itemize}
\end{definition}

\begin{theorem}[PRP in CBC is IND-CPA]
Let $(\O{encode}_\lambda,\O{decode}_\lambda)$ be an encoding scheme and let $f$ be a secure $(\lambda,\lambda)$-secure pseudorandom permutation. Then, the
following encryption scheme $\se_{\text{CBC-f}}$ is IND-CPA-secure.
\begin{center}
\begin{pchstack}
\procedure{$\se_{\text{CBC-f}}.\O{enc}(k,m)$}{
\lambda\gets\abs{k}\\
m'\gets\O{encode}_{\lambda}(m)\\
\pcvar{nonce}\sample\bin^\lambda\\
\pcvar{c}^0\gets\pcvar{nonce}\\
\ell\gets \frac{\abs{m'}}{\lambda}\\
\pcfor i=1..\ell\\
\pcind x^i\gets m'_{i\lambda..(i+1)\lambda-1}\\
\pcind \pcvar{c}_i\gets f(k,x^i\oplus c^{i-1})\\
c\gets (c_0,..,c_\ell)\\
\pcreturn c}
\pchspace
\procedure{$\se_{\text{CBC-f}}.\O{dec}(k,c)$}{
\lambda\gets\abs{k}\\
\ell\gets \frac{\abs{c}}{\lambda}-1\\
\text{Parse }c_0,..,c_\ell\gets c\\
\pcfor i=1..\ell\\
\pcind x^i\gets c^{i-1}\oplus f_{\text{inv}}(k,c^i)\\
m'\gets x^1||..||x^\ell)\\
m\gets \O{decode}_{\abs{k}}(m')\\
\pcreturn m}
\end{pchstack}
\end{center}
\end{theorem}

\begin{theorem}[PRF in CTR is IND-CPA]
Let $(\O{encode}_\lambda,\O{decode}_\lambda)$ be an encoding scheme and let $f$ be a secure $(\lambda,\lambda)$-secure pseudorandom function. Then, the encryption scheme $\se_{\text{CTR-f}}$ is IND-CPA-secure.
\begin{center}
\begin{pchstack}
\procedure{$\se_{\text{CTR-f}}.\O{enc}(k,m)$}{
\lambda\gets\abs{k}\\
\pcvar{nonce}\sample\bin^\lambda\\
m'\gets\O{encode}_\lambda(m)\\
\ell\gets  \frac{\abs{m'}}{\lambda}\\
\pcfor i=1..\ell\\
\pcind \pcvar{pad}_i\gets f(k,\pcvar{nonce}+i)\\
\pcvar{pad}'\gets\pcvar{pad}_1||..||\pcvar{pad}_\ell\\
\pcvar{pad}\gets\pcvar{pad}_{1..\abs{m}}\\
c\gets m \oplus \pcvar{pad}\\
\pcreturn (\pcvar{nonce},c)}
\pchspace
\procedure{$\se_{\text{CTR-f}}.\O{dec}(k,(\pcvar{nonce},c))$}{
\lambda\gets\abs{k}\\
\ell\gets \frac{\abs{c}}{\lambda}\\
\pcfor i=1..\ell\\
\pcind \pcvar{pad}^i\gets f(k,\pcvar{nonce}+i)\\
\pcvar{pad}'\gets\pcvar{pad}^1||..||\pcvar{pad}^\ell\\
\pcvar{pad}\gets\pcvar{pad}_{1..\abs{c}}\\
m'\gets c \oplus \pcvar{pad}\\
m\gets\O{decode}_\lambda(m')\\
\pcreturn m}
\end{pchstack}
\end{center}
\end{theorem}


\paragraph{Generic transformations on symmetric encryption schemes}
\begin{theorem}[IND-CPA]
If $\se$ is an IND-CPA secure symmetric encryption scheme, then $\se_1$ is an IND-CPA secure symmetric encryption scheme.
\begin{center}
\begin{theorem}[AE]
If $\se$ is an IND-CPA secure symmetric encryption scheme, and $\m$ is an UNF-CMA-secure message authentication code, then
$\se_{\text{etm}}$ is an AE-secure symmetric encryption scheme.
\end{theorem}

\begin{pchstack}
        \procedure{$\se_1.\enc(k,m)$}{
          c'\sample\se.\enc(k,m)\\
          c \gets c'||1 \\
          \pcreturn c
        }
        \pcvspace
        \procedure{$\se_1.\dec(k,c)$}{
          c'\gets c[1..\abs{c}-1]\\
          m\gets\se.\dec(k,c')\\
          \pcreturn m
        }
    \pchspace
    \procedure{$\se_{\text{etm}}.\enc(k,m)$}{
			\pcparse (k_\m,k_\se)\gets k\\
			c'\sample\se.\enc(k_\se,m)\\
			\tau\sample\m.\mac(k_\m,c')\\
     c \gets (c',\tau) \\
      \pcreturn c
    }
    \pchspace
    \procedure{$\se_{\text{etm}}.\dec(k,c)$}{
			\pcparse (k_\m,k_\se)\gets k\\
			\pcparse (c',\tau)\gets c\\
			m\gets\se.\dec(k_\se,c')\\
			\pcif 1\gets\verify(k_\m,c',\tau)\ \pcreturn m\\
      \pcelse \pcreturn \bot
    }  
		\end{pchstack}
\end{center}

\end{theorem}